### 2020-05-28 Report/aws_325ghz_study.tex
Work on the report. Extended the discussion section.

\subsection{Noise}
%
The nominal reciever noise temperature, $T_r$ of each band is listed in
Table~\ref{tab:trec}. The noise of data for individual channels is calculated
as
\begin{equation}
  \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
  \label{eq:noise}
\end{equation}
where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
the bandwidth (in terms of IF) of channel and $\Delta t$ is the integration
time.

The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
calibration process. The bandwith applied is the one found in columns 3 of
Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
15\,km resolution at 183\,GHz. This time was estimated to 3\,ms.

\begin{table}[!bt]
  \centering
  \begin{tabular}[b]{c|ccccc}
    Band [GHz]   & 89 & 166 & 183 & 229 & 325 \\
    \hline
    $T_r$ [K]    & 390 & 650 & 650 & {\it 1000}  & 1200 \\
    \hline
  \end{tabular}
  \caption{Assumed reciever noise temperatures. The value for 229\,GHz is
    selected by us, remaining values are present assumptions at Omnisys.}
  \label{tab:trec}
\end{table}

@@

The polarisation response of the bands is not yet determined and for simplicity
``quasi-horisontal'' (defined in same way as for e.g.\ MWS) is throughout
assumed. Antenna temperatures are obtained as:
\begin{equation}
  \label{eq:polrot}
  T_a = T_b^V\sin^2(\theta) + T_b^H\cos^2(\theta)
\end{equation}
where $T_b^V$/$T_b^H$ is the brightness temprature at vertical/horisontal
polarisation, respectively, and $\theta$ is the viewing angle (from nadir).

@@

\subsubsection{Bulk profile database}
%
A database of atmospheric cases was created based on data from CloudSat and
ERA-Interim. The core idea of the approach is to use CloudSat reflectivities to
obtain as realistic vertical profiles of ice hydrometeors and rain as
possible. No external CloudSat retrievals are involved. Instead the CloudSat
reflectivites are mapped to properties for the passive simulations by assuming
a particle size distribution and a particle habit, together denoted as
the particle model. The process involves an inversion of the radar data, but as,
the same particle model is used for that inversion and to map ice water content
(IWC) and rain water content (RWC) to single scattering data when performing
the passive radiative transfer calculations, the impact of clouds on the
simulated AWS data is as realistic as possible. The thin clouds not detected by
CloudSat should not be of relevance for passive measurements frequencies
350\,GHz. Background data (temperature, humidity, 10\,m wind speed, \dots) were
taken from ERA-Interim, for the time and location of the CloudSat data. Liquid
water content (LWC) was taken from ERA-Interim, as CloudSat has no sensitivity
to the hydrometeor category.

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}. A
smaller comparison to RTTOV has been made, that indciated an agreement better
than 0.1\,K in general. Deviations between 0.1 and 0.2\,K were found for some
channels at incidence angles above 40$^\circ$.

@@

In the intermediate region, the simulations have a lower occurance rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

\section{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

@@

In Fig.~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
325\,GHz for the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 325\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

@@

As expected, when the channel is moved away the centre frequency, the weighting
function moves downwards. However, moving the channel from 5\,-\,8\,GHz to
8\,-\,11\,GHz (in IF) results only a small shift, about 400 and 200\,m for the
lower and upper side, respectively. In terms of the resulting double sideband
channel the the shift would be 300\,m. Accordingly, there is little gain by
inforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
between highest and lowest IF is more costly to implement. Albeit small, a
negative consequence of a 8\,-\,11\,GHz channel, compared to 5\,-\,8\,GHz, is
some assymetry in the altitude response between lower and upper sideband. This
assymetry is caused by higher continuum and far wing absorption on the upper
side.

@@

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

@@

\section{Cloud correction by a simple scheme}
%
In this section, the 325\,GHz three channel option is evaluated for detection
and correction of cloud interference in 183\,GHz channels. Combinations of
brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
as a measure of the cloud impact. A regression based approach is used to
estimate the adjustment needed to predict the clear-sky values.

\subsection{Formulation of correction scheme}
\label{sec:correction:scheme}
%
Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
scheme formulates a relationship between the cloud impact in C1 to the TB
differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb1_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
derived from its corresponding counterpart in 325\,GHz channel.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. The black curve represents the line of
      best fit (of green points) as a third order polynomial. Red and green
      color represent the clear and cloudy cases respectively in the simulation
      dataset. The blue vertical line represents correction threshold, $x_{cs}$, for $dtb_{cs} =$
      0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

As an example, the relationship between the TB differences for C1 and C2 and
the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
are used. The two variables have a reasonably strong correlation for small TB
differences, but as the impact of cloud increases, the correlations gets poorer.
The data can be fitted by linear or non-linear models. The fitted model can be
used to obtain the adjustment required to compensate the brightness
temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
assumed to be clear-sky, are not included in the model.

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making filtering in line with \citet{rekha2012potential},
but is also needed in the correction scheme. The latter is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

@@

\subsection{Application of correction scheme}
%
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The average bias values are given in parenthesis in the legend. No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_all}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction. The measurements have been corrected using a cubic model. The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
      \cite{rekha2012potential}.}
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
		noise             		&   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation(std), and measure of skewness of deviations of the measurements to noise-free clear-sky cases. The fraction rejected describes the percentage of cases which are removed. The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).   }
	\label{tab:correction:stats:34:42}
\end{table}
%
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
		&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\	
		\hline
\end{tabular}
\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
\label{tab:correction:stats:34:42:thinned}
\end{table}
%
In this section, we test the applicability of the correction scheme in detail. To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2. Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. As an example, the results from the channel combination AWS-34 and AWS-42 are shown.

@@

The occurrence frequency of the deviations from three models is shown in
Fig.~\ref{fig:correction:c34-42:fit}. The occurence frequency of the measurement
without any filtering or correction is also plotted as reference (orange
color). If all measurements are devoid of any cloud impact, the deviations
should follow the gaussian distribution of noise. However, in real scenarios,
the distribution is skewed due to the impact of clouds. Among the three models, the quadratic and cubic models work
better than the linear model. Both quadratic and cubic models are able to
correct the cloud impact in the measurements, however the values of average
bias indicates that the cubic model performs better. The average deviation in
the dataset is -0.75\,K and after correction with a cubic model, it reduces to
-0.05\,K, while for quadratic model, the average bias after correction is
0.22\,K. For all other results described further, a cubic model is
used. It should also be noted
that since no clear/cloudy classification is included, the peak of the distributions (representing the clear-sky cases) is reduced in the corrected datasets. 
To avoid correcting the clear cases, implementation of clear/cloudy classification is extremely important.

To implement the clear/cloudy classification as discussed in the previous
section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}.

The distribution of the deviations in the pure-filtered data is non-Gaussian. The
right side of the distribution follows measurement noise while the left
side is skewed. The skewness in the distribution is due to cloud impacts which
pass through the clear-sky threshold. A larger skewness in the dataset ``Sreerekha et al'' in comparsion to ``Filtered'' shows that the frequency of misclassfied cases is higher in the approach by \cite{rekha2012potential}. The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through $dtb_{cs}$. After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected. With a fit based cloudy classification, 10.56\% of the cases are classified as cloudy when $dtb_{cs}$
= 1$\sigma$.  Before correction, the average bias for measurements is -0.19\,K
but after correction it reduces to -0.05\,K and -0.09\,K for the two values of
the $dtb_{cs}$ respectively.

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a better
representation of the cloudy cases, we thin the measurement dataset by
removing 50\% of the clear-sky cases. The results from this smaller dataset, before and after filtering/correction are shown in Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the
original dataset, the statistics in the thinned dataset is slightly worse, as
expected. But overall the performance of the correction scheme is comparable. 
For all further analysis presented in this report, the thinned dataset is used.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

>>>>

\subsection{Noise}
%
The nominal receiver noise temperature, $T_r$ of each band is listed in
Table~\ref{tab:trec}. The noise of data for individual channels is calculated
as
\begin{equation}
  \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
  \label{eq:noise}
\end{equation}
where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
scaling factor (see below), $T^i_r$ is the receiver noise temperature of the
channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
the bandwidth (in terms of IF) of channel and $\Delta t$ is the integration
time.

The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
calibration process. The bandwidth applied is the one found in columns 3 of
Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
15\,km resolution at 183\,GHz. This time was estimated to 3\,ms.

\begin{table}[!bt]
  \centering
  \begin{tabular}[b]{c|ccccc}
    Band [GHz]   & 89 & 166 & 183 & 229 & 325 \\
    \hline
    $T_r$ [K]    & 390 & 650 & 650 & {\it 1000}  & 1200 \\
    \hline
  \end{tabular}
  \caption{Assumed receiver noise temperatures. The value for 229\,GHz is
    selected by us, remaining values are present assumptions at Omnisys.}
  \label{tab:trec}
\end{table}

@@

The polarisation response of the bands is not yet determined and for simplicity
``quasi-horizontal'' (defined in same way as for e.g.\ MWS) is throughout
assumed. Antenna temperatures are obtained as:
\begin{equation}
  \label{eq:polrot}
  T_a = T_b^V\sin^2(\theta) + T_b^H\cos^2(\theta)
\end{equation}
where $T_b^V$/$T_b^H$ is the brightness temperature at vertical/horizontal
polarisation, respectively, and $\theta$ is the viewing angle (from nadir).

@@

\subsubsection{Bulk profile database}
%
A database of atmospheric cases was created based on data from CloudSat and
ERA-Interim. The core idea of the approach is to use CloudSat reflectivities to
obtain as realistic vertical profiles of ice hydrometeors and rain as
possible. No external CloudSat retrievals are involved. Instead the CloudSat
reflectivities are mapped to properties for the passive simulations by assuming
a particle size distribution and a particle habit, together denoted as
the particle model. The process involves an inversion of the radar data, but as,
the same particle model is used for that inversion and to map ice water content
(IWC) and rain water content (RWC) to single scattering data when performing
the passive radiative transfer calculations, the impact of clouds on the
simulated AWS data is as realistic as possible. The thin clouds not detected by
CloudSat should not be of relevance for passive measurements frequencies
350\,GHz. Background data (temperature, humidity, 10\,m wind speed, \dots) were
taken from ERA-Interim, for the time and location of the CloudSat data. Liquid
water content (LWC) was taken from ERA-Interim, as CloudSat has no sensitivity
to the hydrometeor category.

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}. A
smaller comparison to RTTOV has been made, that indicated an agreement better
than 0.1\,K in general. Deviations between 0.1 and 0.2\,K were found for some
channels at incidence angles above 40$^\circ$.

@@

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

@@

In Fig.~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
325\,GHz for the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 325\,GHz, but the influence of the surface
reflectivity is considerably lower.  Beside for the tropical case, for
229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

@@

As expected, when the channel is moved away the centre frequency, the weighting
function moves downwards. However, moving the channel from 5\,-\,8\,GHz to
8\,-\,11\,GHz (in IF) results only a small shift, about 400 and 200\,m for the
lower and upper side, respectively. In terms of the resulting double sideband
channel the the shift would be 300\,m. Accordingly, there is little gain by
enforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
between highest and lowest IF is more costly to implement. Albeit small, a
negative consequence of a 8\,-\,11\,GHz channel, compared to 5\,-\,8\,GHz, is
some asymmetry in the altitude response between lower and upper sideband. This
asymmetry is caused by higher continuum and far wing absorption on the upper
side.

@@

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
  \caption{RH weighting functions for the lower (left) and upper (right) side
    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
    bandwidth. The stated frequencies are the centre frequency of each. In
    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
    top-to-bottom in the order given in the legends). }
  \label{fig:wfuns:325ul}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
  \caption{RH weighting functions of the three channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3ch:prel}
\end{figure}
\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
  \caption{RH weighting functions of the four channel option in
    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:4ch:prel}
\end{figure}

@@

\section{Cloud correction by a simple scheme}
\label{sec:simple}
%
In this section, the 325\,GHz three channel option is evaluated for detection
and correction of cloud interference in 183\,GHz channels. Combinations of
brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
as a measure of the cloud impact. A regression based approach is used to
estimate the adjustment needed to predict the clear-sky values.

\subsection{Formulation of correction scheme}
\label{sec:correction:scheme}
%
Let C1 and C2 represent one of the channels each from 183\,GHz and 325\,GHz,
respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
scheme formulates a relationship between the cloud impact in C1 to the TB
differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb1_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. Red and green colour represent the clear
      and cloudy cases respectively in the simulation dataset. The black curve
      represents the line of best fit (of green points) as a third order
      polynomial. The blue vertical line represents the correction threshold,
      $x_{cs}$, for $dtb_{cs} =$ 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

As an example, the relationship between the TB differences for C1 and C2 and
the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
are used. The two variables have a reasonably strong correlation for small TB
differences, but as the impact of cloud increases, the correlations gets
poorer. The data can be fitted by linear or non-linear models. The fitted model
can be used to obtain the adjustment required to compensate the brightness
temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
excluded in the fit. Also, cases with a cloud impact below 0.2\,K (red colour
dots) can be considered as clear-sky, are not included in the model.

It is also important to have a manner for making a clear/cloudy classification
that can be derived from actual measurement data. This is useful for making
filtering in line with \citet{rekha2012potential}, but is also needed in the
correction scheme. The latter is the case as the polynomial fit derived gives a
non-zero correction for clear-sky cases. In Fig.~\ref{fig:fit:c34-42} the
difference between clear-sky values of channel C1 and C2 (red dots) have a mean
close to zero (as the weighting functions are well matched), but this is not
the case for all channel combinations and some general rule for finding a
threshold value (with respect to $x_m$) must be formulated. The polynomial fit
will be used also for this part.

@@

\subsection{Application of correction scheme}
%
In this section, we test the applicability of the correction scheme in detail.
To analyse the performance of the approach, we apply it to correct the
measurements from C1 using data from C2. Without the availability of actual
data, the simulation dataset but with noise added is used mimic the measurements. The
noise for individual channels is calculated according to
Equation~\ref{eq:noise}. As an example, the results from the channel
combination AWS-34 and AWS-42 are shown.

@@

The occurrence frequency of the deviations from three models is shown in
Fig.~\ref{fig:correction:c34-42:fit}. The occurrence frequency of the
measurements without any filtering or correction is also plotted as reference
(orange colour). If all measurements are devoid of any cloud impact, the
deviations should follow the Gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. Among the
three models, the quadratic and cubic models work better than the linear model.
Both quadratic and cubic models are able to correct the cloud impact in the
measurements, however the values of average bias indicates that the cubic model
performs better. The average deviation in the dataset is -0.75\,K and after
correction with a cubic model, it reduces to -0.05\,K, while for quadratic
model, the average bias after correction is 0.22\,K. For all other results
described further, a cubic model is used. It should also be noted that since no
clear/cloudy classification is included, the peak of the distributions
(representing the clear-sky cases) is reduced in the corrected datasets. To
avoid correcting the clear cases, implementation of clear/cloudy classification
is extremely important. [* I still don't get the last part. Do you mean that you
apply the correction on all data? *]

To implement the clear/cloudy classification as discussed in the previous
section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}. [* Why are the yellow lines so
different in Figs.~10 and 11? Maybe we discussed it, but I have then forgot. *]

\begin{figure}[!p]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The mean value of each distribution is given in
      parenthesis in the legend. Cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_all}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected-all (measurement dataset without
      clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are
      filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy
      measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected
      $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
      2$\sigma$), Sreerekha (measurements are filtered according to criteria
      described in \citet{rekha2012potential}).}
	\label{fig:correction:c34-42}
\end{figure}
%
